A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-09 docs/methods/revisions.tex
finalize revisions

\noindent
\comment{In section 3.1, formula 29 is missing a $\Delta s_{j}$}
\begin{itemize}
  \item Fixed
\end{itemize}

@@

We have added the following text at the end of section 5.1:
\begin{quotation}
We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing). Interestingly, stagnation points do indeed recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real physical mechanism (see [46] for discussion).
\end{quotation}

>>>>

\noindent
\comment{In section 3.1, formula 29 is missing a $\Delta s_{j}$}
\begin{itemize}
  \item The arclength term is now included in equation (29).
\end{itemize}

@@

We have added the following text at the end of section 5.1:
\begin{quotation}
We note that the recession of the stagnation points, since the stress
vanishes there, is due entirely to the numerical smoothing (both the
curvature penalization and the stress-distribution smoothing).
Interestingly, stagnation points do indeed recede in laboratory
experiments on erosion [46, 64], leading us to believe that the
numerical smoothing represents a real physical mechanism (see [46] for
discussion).
%
%We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing). Interestingly, stagnation points do indeed recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real physical mechanism (see [46] for discussion).
\end{quotation}
